 

### 2023-03-01 appendix_2.2.Rmd
Revisions to Paper 2 from KK, MM, SV, and JC

panel_a <- facilities_gps_any %>% 
  filter(shape_type == "polygon") %>%
  mutate(area = ifelse(area_km > area_lim, area_lim,
                       ifelse(area_km < 1, 1, 
                              area_km))) %>%
  ggplot() +
  geom_histogram(aes(x=area_km, fill = retain),
                 bins = 100) +
  geom_vline(xintercept = area_lim) +
  labs(x = "Area (km^(2))",
       title = "Polygons of GPS coordinates, by area",
       subtitle = "Smaller areas mean greater agreement across data sources",
       caption = paste0("Line shows threshold limit of ",
                        prettyNum(area_lim, big.mark = ",", scientific = FALSE),
                        " km sq."),
       y = "Count",
       fill = "") +
  theme_classic() +
  theme(axis.title.x = element_markdown(),
        text = element_text(family = "Source Sans Pro"),
        legend.position = "bottom") +
  scale_fill_manual(values = c(col_within_threshold))

@@

panel_a <- facilities_gps_any %>% 
  filter(shape_type == "polygon") %>%
  mutate(area = ifelse(area_km > area_lim, area_lim,
                       ifelse(area_km < 1, 1, 
                              area_km))) %>%
  ggplot() +
  geom_histogram(aes(x=area_km, fill = retain),
                 bins = 100) +
  geom_vline(xintercept = area_lim) +
  labs(x = "Area (km^(2))",
       title = "Polygons of GPS coordinates, by area",
       subtitle = "Smaller areas mean greater agreement across data sources",
       caption = paste0("Line shows threshold limit of ",
                        prettyNum(area_lim, big.mark = ",", scientific = FALSE),
                        " km sq."),
       y = "Count",
       fill = "") +
  theme_classic() +
  theme(axis.title.x = element_markdown(),
        text = element_text(family = "Source Sans Pro"),
        legend.position = "none") +
  scale_fill_manual(values = c(col_within_threshold))

@@

Among polygon groups, the mean area was `r format(round(n_mean_area_polygons,2), big.mark = ",")` km sq, with a maximum area of `r format(round(n_max_area_polygons), big.mark = ",")` km sq. At the threshold of `r format(as.numeric(area_lim), big.mark = ",")` square km., all polygon groups fell within the cut-off. Among line groups, the mean distance between coordinates was `r format(round(n_mean_length,2), big.mark = ",")` km., with a maximum distance of `r format(round(n_max_length), big.mark = ",")` kilometers. At the threshold of `r format(as.numeric(length_lim), big.mark = ",")` km.,  `r format(round(n_length_retained), big.mark = ",")` line groups fell within the cut-off (`r round(as.numeric(n_length_retained)/n_line * 100,0)`% of line groups).

@@

While it would be ideal to obtain precise locations for each facility in our sample, for the purposes of our analysis, an approximate location would be sufficient, given the spatial resolution of the climate data we used. The spatial resolution of ERA-5 and ESA-CCI data is approximately 30 km., meaning that all coordinates within a spatial tile of 30 km. sq. will have the same time series for a given variable. Furthermore, neighboring tiles are unlikely to have extraordinarily different time series, underscoring that close approximate locations would likely result in minimal impact to the analysis versus exact coordinates.

@@

```{r figure_communes_fokontany, include = TRUE, results = TRUE, warning = FALSE, message = FALSE, echo = FALSE, fig.width = 9, fig.height = 8.5, fig.align='center', out.width = '95%',  fig.scap="Communes and fokontany in Madagascar, by area.", out.extra='',  fig.cap="\\label{figure_communes_fokontany}Communes and fokontany in Madagascar, by area. Units colored in teal are within the 225 square kilometer threshold for use in Step 5 of the matching process."}

@@

# Map where area is binary (smaller than value of commune_lim km sq., vs larger)

map_a <- map_mdg_3 %>%
  mutate(area_km = as.numeric(st_area(geometry)/1000000)) %>%
  mutate(area_km_1 = ifelse(area_km <= commune_lim,
                            paste0("<= ",
                                   prettyNum(commune_lim, big.mark = ",", scientific = FALSE),
                                   " km sq."),
                            paste0("> ",
                                   prettyNum(commune_lim, big.mark = ",", scientific = FALSE),
                                   " km sq.")))%>%
  ggplot(aes(geometry = geometry))  +
  geom_sf(size = 0.2,
          aes(fill = area_km_1),
          color = col_grey_light) +
  geom_sf(data = map_mdg_2,
          size = 0.2,
          color = col_grey_med,
          fill = NA) +
  geom_sf(data = map_mdg_1,
          size = 0.2,
          color = col_black,
          fill = NA) +
  theme_void() +
  theme(text = element_text(family = "Source Sans Pro")) +
  labs(fill = "Area (km sq.)",
       title = "Communes",
       subtitle = "(second smallest admin. unit in Madagascar)") +
  scale_fill_manual(values = c(col_within_threshold, col_grey_lightest))

@@

map_b <- map_mdg_4 %>%
  mutate(area_km = as.numeric(st_area(geometry)/1000000)) %>%
  mutate(area_km_1 = ifelse(area_km <= fokontany_lim,
                            paste0("<= ",
                                   prettyNum(fokontany_lim, big.mark = ",", scientific = FALSE),
                                   " km sq."),
                            paste0("> ",
                                   prettyNum(fokontany_lim, big.mark = ",", scientific = FALSE),
                                   " km sq.")))%>%
  ggplot(aes(geometry = geometry))  +

  geom_sf(size = 0.2,
          aes(fill = area_km_1),
          color = col_grey_lightest) +
    geom_sf(data = map_mdg_3,
          size = 0.2,
          color = col_grey_light,
          fill = NA) +
  geom_sf(data = map_mdg_2,
          size = 0.2,
          color = col_grey_med,
          fill = NA) +
  geom_sf(data = map_mdg_1,
          size = 0.2,
          color = col_black,
          fill = NA) +
  theme_void() +
  theme(text = element_text(family = "Source Sans Pro")) +
  labs(fill = "Area (km sq.)",
       title = "Fokontany",
       subtitle = "(smallest admin. unit in Madagascar)") +
  scale_fill_manual(values = c(col_within_threshold, col_grey_lightest))

@@

Comparing the geolocated coordinates to validated coordinates for each facility, the mean distance between coordinates in the validation sample was `r format(round(validation_mean_dist,2), big.mark = ",")` km., with a maximum distance of approximately `r format(round(validation_max_dist, 1), big.mark = ",")` kilometers. The distance between geolocated and validated coordinates for each of the facilities in the validation sample is reported in Table S2.11.

>>>>

panel_a <- facilities_gps_any %>% 
  filter(shape_type == "polygon") %>%
  mutate(area = ifelse(area_km > area_lim, area_lim,
                       ifelse(area_km < 1, 1, 
                              area_km))) %>%
  ggplot() +
  geom_histogram(aes(x=area_km, fill = retain),
                 bins = 100) +
  geom_vline(xintercept = area_lim) +
  labs(x = "Area (km^(2))",
       title = "Polygons of GPS coordinates, by area",
       subtitle = "Smaller areas mean greater agreement across data sources",
       caption = paste0("Line shows threshold limit of ",
                        prettyNum(area_lim, big.mark = ",", scientific = FALSE),
                        " km²"),
       y = "Count",
       fill = "") +
  theme_classic() +
  theme(axis.title.x = element_markdown(),
        text = element_text(family = "Source Sans Pro"),
        legend.position = "bottom") +
  scale_fill_manual(values = c(col_within_threshold))

@@

panel_a <- facilities_gps_any %>% 
  filter(shape_type == "polygon") %>%
  mutate(area = ifelse(area_km > area_lim, area_lim,
                       ifelse(area_km < 1, 1, 
                              area_km))) %>%
  ggplot() +
  geom_histogram(aes(x=area_km, fill = retain),
                 bins = 100) +
  geom_vline(xintercept = area_lim) +
  labs(x = "Area (km^(2))",
       title = "Polygons of GPS coordinates, by area",
       subtitle = "Smaller areas mean greater agreement across data sources",
       caption = paste0("Line shows threshold limit of ",
                        prettyNum(area_lim, big.mark = ",", scientific = FALSE),
                        " km²"),
       y = "Count",
       fill = "") +
  theme_classic() +
  theme(axis.title.x = element_markdown(),
        text = element_text(family = "Source Sans Pro"),
        legend.position = "none") +
  scale_fill_manual(values = c(col_within_threshold))

@@

Among polygon groups, the mean area was `r format(round(n_mean_area_polygons,2), big.mark = ",")` km², with a maximum area of `r format(round(n_max_area_polygons), big.mark = ",")` km². At the threshold of `r format(as.numeric(area_lim), big.mark = ",")` square km., all polygon groups fell within the cut-off. Among line groups, the mean distance between coordinates was `r format(round(n_mean_length,2), big.mark = ",")` km, with a maximum distance of `r format(round(n_max_length), big.mark = ",")` km. At the threshold of `r format(as.numeric(length_lim), big.mark = ",")` km,  `r format(round(n_length_retained), big.mark = ",")` line groups fell within the cut-off (`r round(as.numeric(n_length_retained)/n_line * 100,0)`% of line groups).

@@

While it would be ideal to obtain precise locations for each facility in our sample, for the purposes of our analysis, an approximate location would be sufficient, given the spatial resolution of the climate data we used. The spatial resolution of ERA-5 and ESA-CCI data is approximately 30 km., meaning that all coordinates within a spatial tile of 30 km² will have the same time series for a given variable. Furthermore, neighboring tiles are unlikely to have extraordinarily different time series, underscoring that close approximate locations would likely result in minimal impact to the analysis versus exact coordinates.

@@

```{r figure_communes_fokontany, include = TRUE, results = TRUE, warning = FALSE, message = FALSE, echo = FALSE, fig.width = 9, fig.height = 8.5, fig.align='center', out.width = '95%',  fig.scap="Communes and fokontany in Madagascar, by area.", out.extra='',  fig.cap="\\label{figure_communes_fokontany}Communes and fokontany in Madagascar, by area. Units colored in teal are within the 225 km² threshold for use in Step 5 of the matching process."}

@@

# Map where area is binary (smaller than value of commune_lim km², vs larger)

map_a <- map_mdg_3 %>%
  mutate(area_km = as.numeric(st_area(geometry)/1000000)) %>%
  mutate(area_km_1 = ifelse(area_km <= commune_lim,
                            paste0("<= ",
                                   prettyNum(commune_lim, big.mark = ",", scientific = FALSE),
                                   " km²"),
                            paste0("> ",
                                   prettyNum(commune_lim, big.mark = ",", scientific = FALSE),
                                   " km²")))%>%
  ggplot(aes(geometry = geometry))  +
  geom_sf(size = 0.2,
          aes(fill = area_km_1),
          color = col_grey_light) +
  geom_sf(data = map_mdg_2,
          size = 0.2,
          color = col_grey_med,
          fill = NA) +
  geom_sf(data = map_mdg_1,
          size = 0.2,
          color = col_black,
          fill = NA) +
  theme_void() +
  theme(text = element_text(family = "Source Sans Pro")) +
  labs(fill = "Area (km²)",
       title = "Communes",
       subtitle = "(second smallest admin. unit in Madagascar)") +
  scale_fill_manual(values = c(col_within_threshold, col_grey_lightest))

@@

map_b <- map_mdg_4 %>%
  mutate(area_km = as.numeric(st_area(geometry)/1000000)) %>%
  mutate(area_km_1 = ifelse(area_km <= fokontany_lim,
                            paste0("<= ",
                                   prettyNum(fokontany_lim, big.mark = ",", scientific = FALSE),
                                   " km²"),
                            paste0("> ",
                                   prettyNum(fokontany_lim, big.mark = ",", scientific = FALSE),
                                   " km²")))%>%
  ggplot(aes(geometry = geometry))  +

  geom_sf(size = 0.2,
          aes(fill = area_km_1),
          color = col_grey_lightest) +
    geom_sf(data = map_mdg_3,
          size = 0.2,
          color = col_grey_light,
          fill = NA) +
  geom_sf(data = map_mdg_2,
          size = 0.2,
          color = col_grey_med,
          fill = NA) +
  geom_sf(data = map_mdg_1,
          size = 0.2,
          color = col_black,
          fill = NA) +
  theme_void() +
  theme(text = element_text(family = "Source Sans Pro")) +
  labs(fill = "Area (km²)",
       title = "Fokontany",
       subtitle = "(smallest admin. unit in Madagascar)") +
  scale_fill_manual(values = c(col_within_threshold, col_grey_lightest))

@@

Comparing the geolocated coordinates to validated coordinates for each facility, the mean distance between coordinates in the validation sample was `r format(round(validation_mean_dist,2), big.mark = ",")` km., with a maximum distance of approximately `r format(round(validation_max_dist, 1), big.mark = ",")` km. The distance between geolocated and validated coordinates for each of the facilities in the validation sample is reported in Table S2.11.
